\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-10-28 cover-letter/cover-letter.Rmd
added cover letter

We have undertaken major revision on our manuscript titled, "Calendar-based graphics for visualizing people's daily schedules," based on reviewers' comments.

The major changes include two new sections: a subsection "2.4 Reasons to use calendar-based graphics" to explain why calendar displays are useful and when to use them, and a section "3 Making calendar facets" to describe a new calendar faceting method `facet_calendar()`, that extends **ggplot2** intervals and complements the existing function `frame_calendar()`.

@@

We believe that this manuscript has been significantly improved, that is a good fit for the Journal of Computational and Graphical Statistics.

>>>>

We have done minor revision on our manuscript titled, "Calendar-based graphics for visualizing people's daily schedules," based on associate editor and reviewers' comments.

@@

We believe that this manuscript has been improved, that is a good fit for the Journal of Computational and Graphical Statistics.
